\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-09-15 challenge.tex
reword

The tension results from the duality between variants and records.
Existing family-polymorphism mechanisms are designed for record-like
language constructs like classes and objects; inductive types, by
contrast, are variant-like.

>>>>

The tension results from the duality between variants and records.
For record-like language constructs (e.g., classes and objects), it is
safe for an extension to add more fields.
By contrast, variant-like language constructs (e.g., inductive types)
do not automatically enjoy safe, modular addition of constructors.
